---
title: "Welcome to r2social: Inclusion of social sharing and connect buttons on a page"
author: "Obinna N. Obianom"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Welcome to r2social: Inclusion of social sharing and connect buttons on a page}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## The goal of this new R package is to provide functions that allow the inclusion of share and connect buttons on any page. This has been tested in Rmarkdown documents as well as on simply Shiny applications. See the examples folder of this package.

Constitutes the following features
  
      + Share link buttons
      
      + Connect buttons
      
      + Hyperlink buttons


### Installation and Library Attachment

The r2social package is available on CRAN and can be installed as shown below

`install.packages(r2social)`

Attach library 

`library(r2social)`

### Use

The r2social can be used within the R Markdown document or in Shiny applications as shown below


#### Include the scripts and stylesheets

```{r eval=TRUE,echo=TRUE}
r2social.scripts()
```

#### Use in Shiny Application

```{r}

library(shiny)
library(r2social)

ui <- fluidPage(
  
  r2social.scripts(),
  
  #include share buttons
  shareButton(link = "http://rpkg.net", position = "left"),
  shareButton(link = "http://obianom.com", position = "right"),
  shareButton(link = "http://google.com", position = "inline"),
  
  #include customized connect buttons where you specify direct links
  connectButton(link = "http://rpkg.net", visit.us=TRUE, position = "inline"),
  connectButton(link = "https://www.linkedin.com/in/oobianom", linkedin=TRUE, position = "inline"),
  connectButton(link = "https://twitter.com/R2Rpkg", twitter=TRUE, position = "inline",display.inline = FALSE),
  connectButton(link = "https://twitter.com/R2Rpkg", twitter=TRUE, position = "inline",display.inline = FALSE)
)


```

#### Use in Rmarkdown documents

```{r}

library(r2social)

r2social.scripts()

# include share buttons
shareButton(link = "http://rpkg.net", position = "left")
shareButton(link = "http://obianom.com", position = "right")
shareButton(link = "http://66pharm.com", position = "inline")

# include customized connect buttons where you specify direct links
connectButton(link = "http://rpkg.net", visit.us = TRUE, position = "inline")
connectButton(link = "https://www.linkedin.com/in/oobianom", linkedin = TRUE, position = "inline")
connectButton(link = "https://twitter.com/R2Rpkg", twitter = TRUE, position = "inline", display.inline = FALSE)
connectButton(link = "https://twitter.com/R2Rpkg", twitter = TRUE, position = "inline", display.inline = FALSE)



```


## Full examples and documentation

 + https://r2social.obi.obianom.com
